---
title: "NLP"
author: "Charles Lang"
date: "2/23/2017"
output: html_document
---

## Libraries
```{r}
#Make sure you install and load the following libraries

library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)
library(tidyverse) #You will need the full tidyverse package not tidyr and dyplr separately
library(topicmodels)

#IF USING A MAC PLEASE RUN THIS CODE
Sys.setlocale("LC_ALL", "C")
```

## In the class-notes folder you will find real csv files exported from real student's note taking in this class. Import all document files and the list of weeks file
```{r}
library(tidyverse)

#Create a list of all the files, then loop over file list importing them and binding them together
D1 <- list.files(path = "/YOUR FILE PATH/class-notes/",
               pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_csv(., col_types = cols(.default = "c"))) 
  
```

## Step 1 - Clean
```{r}
#Separate out the variables of interest
D1 <- select(D1, Title, Notes)

#Remove the htlm tags from your text
D1$Notes <- gsub("<.*?>", "", D1$Notes)
D1$Notes <- gsub("nbsp", "" , D1$Notes)
D1$Notes <- gsub("nbspnbspnbsp", "" , D1$Notes)
D1$Notes <- gsub("<U+00A0><U+00A0><U+00A0>", "" , D1$Notes)

#Merge the weeks data with your notes data so that each line has a week attributed to it 

#Also remove readings not belonging to the class (IE - that are NA for week)

```

## Step 2 - Process text using the tm package
```{r}
#Convert the data frame to the corpus format that the tm package uses
corpus <- VCorpus(VectorSource(D1$Notes))
#Remove spaces
corpus <- tm_map(corpus, stripWhitespace)
#Convert to lower case
corpus <- tm_map(corpus, tolower)
#Remove pre-defined stop words ('the', 'a', etc)
corpus <- tm_map(corpus, removeWords, stopwords('english'))
#Convert words to stems ("education" = "edu") for analysis, for more info see  http://tartarus.org/~martin/PorterStemmer/
corpus <- tm_map(corpus, stemDocument)
#Remove numbers
corpus <- tm_map(corpus, removeNumbers)
#remove punctuation
corpus <- tm_map(corpus, removePunctuation)
#Convert to plain text for mapping by wordcloud package
corpus <- tm_map(corpus, PlainTextDocument, lazy = TRUE)

#Convert corpus to a term document matrix - so each word can be analyzed individuallly
tdm.corpus <- TermDocumentMatrix(corpus)

#Note: we won't remove plural words here, plural words in English tend to be highly irregular and difficult to extract reliably
```

What processing steps have you conducted here? Why is this important? Are there any other steps you should take to process your text before analyzing?

## Step 3 - Find common words
```{r}
#The tm package can do some simple analysis, like find the most common words
findFreqTerms(tdm.corpus, lowfreq=500, highfreq=Inf)
#We can also create a vector of the word frequencies that can be useful to see common and uncommon words
word.count <- sort(rowSums(as.matrix(tdm.corpus)), decreasing=TRUE)
word.count <- data.frame(word.count)
#Look at the word.count dataframe
```

## Generate a Word Cloud

### ColorBrewer
ColorBrewer is a useful tool to help you choose colors for visualizations that was originally built for cartographers. On the ColorBrewer website (http://colorbrewer2.org/#) you can test different color schemes or see what their preset color schemes look like. This is very useful, especially if you are making images for colorblind individuals. 
```{r}
#Define the colors the cloud will use
col=brewer.pal(6,"Dark2")
#Generate cloud, make sure your window is large enough to see it
wordcloud(corpus, min.freq=500, scale=c(5,2),rot.per = 0.25,
          random.color=T, max.word=45, random.order=F,colors=col)
```

# Sentiment Analysis

### Match words in corpus to lexicons of positive & negative words
```{r}
#Upload positive and negative word lexicons
positive <- readLines("positive-words.txt")
negative <- readLines("negative-words.txt")

#Search for matches between each word and the two lexicons
D1$positive <- tm_term_score(tdm.corpus, positive)
D1$negative <- tm_term_score(tdm.corpus, negative)

#Generate an overall pos-neg score for each line
D1$score <- D1$positive - D1$negative

```

## Using ggplot Generate a visualization of the mean sentiment score over weeks, remove rows that have readings from other classes (NA for weeks). You will need to summarize your data to achieve this.
```{r}

```

# LDA Topic Modelling

Using the same csv file you have generated the LDA analysis will treat each row of the data frame as a document. Does this make sense for generating topics?

```{r}
#Term Frequency Inverse Document Frequency
dtm.tfi <- DocumentTermMatrix(corpus, control = list(weighting = weightTf))

#Remove very uncommon terms (term freq inverse document freq < 0.1)
dtm.tfi <- dtm.tfi[,dtm.tfi$v >= 0.1]

#Remove non-zero entries
rowTotals <- apply(dtm.tfi , 1, sum) #Find the sum of words in each Document
dtm.tfi2   <- dtm.tfi[rowTotals> 0, ] #Divide by sum across rows

#Identify rows with zero entries
which(rowTotals %in% c(0))

#Remove these rows from original dataset
#D1 <- D1[-c(?,?),]

#Generate LDA model, k is the number of topics and the seed is a random number to start the process
lda.model = LDA(dtm.tfi, k = 5, seed = 150)

#Which terms are most common in each topic
terms(lda.model, k = 10) 

#Identify which documents belong to which topics based on the notes taken by the student
D1$topic <- topics(lda.model)

```

What does an LDA topic represent? 

# Final Task 

Find a set of documents, perhaps essays you have written or articles you have available and complete an LDA analysis of those documents. Does the method group documents as you would expect?

